### 2014-06-19 Docs/compilers/compilers.tex
compiler updates

 A separate issue is that the ``volume'' reported by {\tt
 multifab\_volume()} seems to be wrong.  For a single level run, it
 should just be $\mathtt{nx} \times \mathtt{ny} \times \mathtt{nz}$,
 but the value reported is incorrect.  This issue only manifests when
 using OpenMP, so it is likely related to the OpenMP loop in {\tt
 boxarray\_volume()}, which is called by \code{multifab\_volume()}.
 In Cray 8.2.4 the problem appears to be resolved, with  
 \code{\tt multifab\_volume()} returning the correct cell count.

\item Cray 8.2.6 on NERSC Edison seems to work well with OpenMP.

@@

Probably the best compilers for \maestro.  
Some notes:
\begin{itemize}
\item gfortran 4.4.3 dies with an out of bounds error in multigrid for
2+ level runs with effective 128$^3$ resolution or better.
\item gfortran 4.5 has no known issues.
\item gfortran 4.6.1--4.6.3 on Fedora (15 and 16) have a bug that 
shows up in multi-processor, multilevel runs ({\tt toy\_convect} on 4
processors, with {\tt inputs\_2d\_ml.test} for instance).  The symptom
is a crash during initialization with the message that ``message sizes
do not match across processes in the collective'' in a {\tt
parallel\_bcast} call.  This is in {\tt cluster\_f.f90}, and the issue
seems to be a multiplication error in computing the size to allocate
{\tt bxs}.  The bug is not present when you compile in debug mode, so
it seems to be related to optimization.
\item gfortran 4.7.1 (prerelease) seems to have fixed the above issue,
but now wdconvect with 2-level, effective 768$^3$ dies due to an
unknown seg fault at the beginning of the run.
\end{itemize}

>>>>

 \item A separate issue is that the ``volume'' reported by {\tt
 multifab\_volume()} seems to be wrong.  For a single level run, it
 should just be $\mathtt{nx} \times \mathtt{ny} \times \mathtt{nz}$,
 but the value reported is incorrect.  This issue only manifests when
 using OpenMP, so it is likely related to the OpenMP loop in {\tt
 boxarray\_volume()}, which is called by \code{multifab\_volume()}.
 In Cray 8.2.4 the problem appears to be resolved, with  
 \code{\tt multifab\_volume()} returning the correct cell count.

\item Cray 8.2.5 works well on titan/OLCF with MPI/OpenMP
\item Cray 8.2.6 works well on edison/NERSC with MPI/OpenMP.

@@

Probably the best compilers for \maestro.  
Some notes:
\begin{itemize}
\item gfortran 4.4.3 dies with an out of bounds error in multigrid for
2+ level runs with effective 128$^3$ resolution or better.
\item gfortran 4.5 has no known issues.
\item gfortran 4.6.1--4.6.3 on Fedora (15 and 16) have a bug that 
shows up in multi-processor, multilevel runs ({\tt toy\_convect} on 4
processors, with {\tt inputs\_2d\_ml.test} for instance).  The symptom
is a crash during initialization with the message that ``message sizes
do not match across processes in the collective'' in a {\tt
parallel\_bcast} call.  This is in {\tt cluster\_f.f90}, and the issue
seems to be a multiplication error in computing the size to allocate
{\tt bxs}.  The bug is not present when you compile in debug mode, so
it seems to be related to optimization.
\item gfortran 4.7.1 (prerelease) seems to have fixed the above issue,
but now wdconvect with 2-level, effective 768$^3$ dies due to an
unknown seg fault at the beginning of the run.

\item There are no known issues with gfortran 4.8.x
